Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2019-12-04 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Minor update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2913 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0766b25b739f23cd7417072fe9b2f94fea1f79ee

The performance of the novel circular trees and forests are assessed in a real case study for shortterm
probabilistic wind direction forecasting at two airports with different site characteristics.
As benchline models, probabilistic climatology and perstistency models, as well as a state-of-the-art
circular GLM are evaluated based on proper scoring rules.
In summary, the circular trees and forests have the highest predictive performance in this setting.
For cases without changes in the wind regime, lagged response values provide already
highly skillful estimates leading to good performance of the persistency model for shortterm wind direction forecasts. While in these cases the trees and forests also benefit from the highly informative lagged response, they can compensate for a lower information of this covariate by incorporating other quantities and possible interactions of these, contrary to the persistency model (see Figure~\ref{fig:boxplot_crpsskill}).
Hence, the tree-based models provide reliable forecasts in all tested meterological settings.
For operational use, a possible extension could be the incorporation of numerical weather predictions as (additional) covariates. While this probably only slightly improves the predictive skill for short leadtimes, it possibly extends the potential forecast range of the different methods.

Another possible improvement for obtaining more parsimonious circular trees is
to consider splitting circular covariates into two circle segments by searching
two split points simultaneously rather than sequentially at different depths.
While this might slightly improve the predictive performance of circular trees,
this should not affect the performance  of circular forest, as these still typically 
consist of very large trees with many different splits.

>>>>

The performance of the novel circular trees and forests are assessed in a real case study for shortterm
probabilistic wind direction forecasting at two airports with different site characteristics.
As benchline models, probabilistic climatology and perstistency models, as well as a state-of-the-art
circular GLM are evaluated based on proper scoring rules.
In summary, the circular trees and forests have the highest predictive performance in this setting.
For cases without changes in the wind regime, lagged response values provide already
highly skillful estimates leading to good performance of the persistency model for shortterm wind direction forecasts. While in these cases the trees and forests also benefit from the highly informative lagged response, they can compensate for a lower information of this covariate by incorporating other quantities and possible interactions of these, contrary to the persistency model (see Figure~\ref{fig:boxplot_crpsskill}).
Hence, the tree-based models provide reliable forecasts in all tested meterological settings.
For operational use, a possible extension could be the incorporation of numerical weather predictions as (additional) covariates. While this probably only slightly improves the predictive skill for short leadtimes, it possibly extends the potential forecast range of the different methods. 
Another possible improvement for obtaining more parsimonious circular trees is
to consider splitting circular covariates into two circle segments by searching
two split points simultaneously rather than sequentially at different depths.
While this might slightly improve the predictive performance of circular trees,
this should not affect the performance  of circular forest, as these
consist of very large trees with many different splits.
